\section{Manual testing} I have asked four people to do the manual user acceptance tests of the functionalities I have implemented. The implementation does not contain many UI components, but is focused on the proper functioning. As it was very important for me to make sure, that I get all the features tested I have offered each tester a scenario, which is shown in Table 6.1. Moreover, I have created a list of the requirements shown below, which they also must use for testing the features in random order and also estimate the look for a few UI components. Besides, I have defined the roles that testers should use for testing and the conditions they need to establish.  

\

\paragraph*{Roles.} The test must be provided for the role I have assigned to the tester for checking the correctness of the access control system. Each tester has one of the next four roles assigned: admin, guarantor, teacher, and student. All testers have different roles assigned.

\

\paragraph*{Conditions.} 
\begin{itemize}
    \item  Client and Server applications are running.
    \item  Course was imported, the user's username exists in the database for that course and has an assigned role for the imported course.
    \item  The expiration time of the access token is recommended to be mocked for five minutes.
\end{itemize}

\

\paragraph*{Requirements for the application.} 
\begin{itemize}
    \item No access to the application for non-authorized users.
    \item Clear and fast login procedure.
    \item Access control responds to the role permissions.
    \item Application allows persistent authorization across the page reloads.
    \item Application does not require repeated authorization after the access token expiration (five minutes in a case of a mocked expiration time instructed in the conditions section or sixty minutes if not mocked).
    \item Logout procedure includes the modal window for submitting the option to log out.
    \item Logout process is clear and fast.
    \item Login and logout UI components are good-looking.
\end{itemize}



\newpage
\noindent \textbf{Offered scenario.} 

\begin{table}[ht]
\begin{tabular}{|c|l|l|}
\hline
\multicolumn{1}{|l|}{} & Test Step:                                                                                                                                                           & Expected result:                                                                                                         \\ \hline
1.                     & \begin{tabular}[c]{@{}l@{}}Try to access the home\\ page of the application.\end{tabular}                                                                            & Redirection to the login page.                                                                                           \\ \hline
2.                     & Clicks on the login button.                                                                                                                                          & Redirected to the login form.                                                                                            \\ \hline
3.                     & \begin{tabular}[c]{@{}l@{}}Submitted login form with\\ valid credentials.\end{tabular}                                                                               & Redirected to the home page.                                                                                             \\ \hline
4.                     & \begin{tabular}[c]{@{}l@{}}Control all the displayed \\ navigation tabs to be \\ correct for your role.\end{tabular}                                                 & Tabs are displayed correctly.                                                                                            \\ \hline
5.                     & Refresh the page.                                                                                                                                                    & \begin{tabular}[c]{@{}l@{}}Page was successfully refreshed, \\ user still has access to the \\ application.\end{tabular} \\ \hline
6.                     & \begin{tabular}[c]{@{}l@{}}Leave a browser page with an\\ application open for 5 minutes\\ and then click to one of the tabs \\ from the navigation bar\end{tabular} & \begin{tabular}[c]{@{}l@{}}Component loaded by the path\\ of navigation tab.\end{tabular}                                \\ \hline
7.                     & Click the logout button.                                                                                                                                             & \begin{tabular}[c]{@{}l@{}}The modal window displayed and \\ requires the submission to log out.\end{tabular}            \\ \hline
8.                     & Submit.                                                                                                                                                              & Redirected to the login page.                                                                                            \\ \hline
\end{tabular}
\caption{\label{test-scenario}Scenario for manual testing.}
\end{table}

\paragraph*{Results.} 

\begin{itemize}
    \item \emph{Tester 1. Anonymous with the admin role}
        \begin{itemize}
            \item \emph{Scenario:} passed
            \item \emph{Requirements:} passed
            \item \emph{Feedback:} "Page reload takes longer from time to time. Access control works good as well as login and logout."
        \end{itemize}
    \item \emph{Tester 2. Bc. Darya Litvinenka with the guarantor role}
            \begin{itemize}
            \item \emph{Scenario:} passed 
            \item \emph{Requirements:} passed
            \item \emph{Feedback:} "Everything works fine. "
        \end{itemize}
    \item \emph{Tester 3. Bc. Adam Vonášek with the teacher role}
            \begin{itemize}
            \item \emph{Scenario:} passed
            \item \emph{Requirements:} passed
            \item \emph{Feedback:} "I did't find any problem and would rate the experience usage as positive. The only thing I'm not sure about is the access control for my role as the application doesn't have many tabs and functionalities yet."
        \end{itemize}
    \item \emph{Tester 4. Anonymous with the student role}
            \begin{itemize}
            \item \emph{Scenario:} passed
            \item \emph{Requirements:} passed
            \item \emph{Feedback:} "The speed of the login was not very fast. Otherwise i didnt have a problem with anything."
        \end{itemize}
\end{itemize}
